\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}  % Style options: casual, classic, banking, oldstyle, fancy
\moderncvcolor{orange}     % Color options: blue, orange, green, red, purple, grey, black

% Character encoding
\usepackage[utf8]{inputenc}  % Unicode support

% Adjust the page margins
\usepackage[scale=0.85]{geometry}

% Personal Information
\name{Jacob}{Ming Xing Runyan}
\title{Software Engineer} % Job title/career
\address{816 Dona Avenue}{Sunnyvale, CA 94087} % Address
\phone[mobile]{+1~(669)~224~9483} % Mobile phone
\email{runyanjake@gmail.com} % Email address
\homepage{jake.runyan.dev} % Website
\social[linkedin]{linkedin.com/in/runyanjake}
\social[github]{github.com/runyanjake}

% Start of document
\begin{document}

% Title (name) on top of the resume
\makecvtitle

% Section: Experience
\section{Experience}

\cventry{2018--Present}{Software Engineer}{Egnyte}{Mountain View, CA}{\textit{Full-time}}{
\begin{itemize}
    \item \textbf{API Caching}: 
    Implemented Nginx caching on metadata of large folder listings, reducing X\% load on a heavily loaded central Memcache cluster.
    Identified the noisy internal caller, request patterns, and provided a solution tailored to fix the problem case,
    working with multi national teams to test, scale, and maintain the solution.
    \item \textbf{Service Design/Deployment}: 
    Leveraged Google Cloud Storage (GCP) and Firestore (FS) to store alternate file streams from Microsoft (MS) products, a component of our coauthoring solution.
    Researched and made design decision between native and Datastore version of FS.
    \\
    Contributed to rapid adoption of the solution, which became a leader in several internal calls, and noted value add for marketing.
    In an organization actively switching to microservices, was one leading project to deploy as a standalone new service. Documented steps and pitfalls for those following.
    \item \textbf{Compliance}: 
    Contributed to multiple teams' efforts to ensure CMMC compliance for securing the usage of GCP resources. 
    Supported the BigTable client conversion to Implicit Authentication, aligning with compliance standards.
    Use of Semgrep tooling to manage, fix, and report security alerts.
    \item \textbf{Work with Legacy Code}: 
    One of two backend engineers providing internal support for the unification of the Collaborate and Secure \& Govern projects under the "Platform" rebranding. 
    Contributed to the unification of the internal user management service, streamlining processes across projects.
    \item\textbf{Support}: 
    Triage of incidents, and support/feature requests for monitored services. Experience using logging (Kibana) and monitoring (OpenTSDB/Prometheus/Grafana) to debug issues.
\end{itemize}}

% Section: Education
\section{Education}

\cventry{2015--2018}{Bachelor of Science, Computer Science}{University of California, Santa Cruz}{}{}{
Graduated ahead of schedule in 3 years from the Baskin School of Engineering. 
Relevant coursework: Algorithms, Data Structures, Databases, Operating Systems, Artificial Intelligence.}

% Section: Skills
\section{Skills}
\cvitem{Java}{5+ years developing Spring/Spring Boot projects in Maven.}
\cvitem{Python}{5+ years use for writing tests, as a scripting language, and for standalone projects.}
\cvitem{Cloud}{Google Cloud Platform, some AWS.}
\cvitem{Machine Learning/AI}{Basic knowledge of perceptron/NN architecture, some experience with Tensorflow/PyTorch. Proficient using GenAI in personal/professional work (ComfyUI, LMStudio, etc)}
\cvitem{Misc}{Other languages include C/C++/Lua. Experience with a few SQL/NoSQL types.}

% Section: Projects
\section{Projects}
\cvitem{Web Development}{\textbf{Frontend:} Web development for a variety of projects, in a variety of frameworks including React, Docusaurus, Flask, and plain old html/css/js.}
\cvitem{Systems \& Hardware}{\textbf{Homelabbing}: Multiple iterations of a personal homelab (see: r/homelab), used for remote computation, video rendering jobs, and hosting personal projects/websites. Experience with DNS settings, storage solutions (ZFS RAIDz1) and Traefik/Nginx load balancing.}
% End of document
\end{document}